% LaTeX boilerplates from [resumake.io](https://resumake.io)

\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[margin=1in]{geometry}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Large \scshape {Tubagus Muhammad Reza Handzalah}}\\
	rezahandzalah@protonmail.com $\cdot$ +6281312646370 $\cdot$ linkedin.com/in/reza-handzalah\\
\end{center}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{IDEMIA}\hfill Aug 2019 | present\\
\textit{as Software Engineer @ Card Personalization System (CPS), Jakarta Office}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Develops and tests CPS Mobile Card Configurator graphical user interface legacy application.
\end{itemize}
\vspace{1mm}

\textbf{PT Telekomunikasi Indonesia}\hfill Jan 2019 | Jun 2019\\
\textit{as Data Scientist Intern @ Divisi Digital Service}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Assigned to GCP Document Recognition project. 
    \item My contribution was developing the system's command line interface application.
\end{itemize}
\vspace{1mm}



\textbf{PT Radar Telekomunikasi Indonesia (RTI)} \hfill Apr 2018 | Jun 2018\\
\textit{as Intern}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item GUI project (Microsoft Visual Studio C\#) for radar antenna motor.
  
\end{itemize}

\textbf{Optical Communication System Lab}\hfill Aug 2017 | Aug 2018\\
\textit{as Research Assistant Coordinator (undergraduate)} \\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
  \item Organized FTTH Drafter Training, paid optical communication system training event with 30 participants (mostly final-year undergraduate students).
  \item Competed in Ristekdikti PKM. My team managed to get 2 proposals accepted.
  
\end{itemize}


%==== Projects ====%
\header{Projects}

{\textbf{tapol.org Responsive Design}} \hfill {\sl html, css}\\https://tapol-org-clone.now.sh/\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Recreated tapol.org website and made it responsive. Desktop-first design.
\end{itemize}

\vspace*{2mm}
{\textbf{gojek.com Website Clone}} \hfill {\sl html, css, js (svelte)}\\https://gojek-com-clone.now.sh/\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Assembled image and font assets of www.gojek.com to recreate the original.
    \item Blog post: 2 Tiny Improvement Ideas for gojek.com Website
\end{itemize}

\vspace*{2mm}
{\textbf{Grid Collage Maker}} \hfill {\sl js (nativescript)}\\link/to/apk\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Quickly make collages in your phone.
\end{itemize}

\vspace*{2mm}

{\textbf{xls2json}} \hfill {\sl python}\\https://pypi.org/project/xls2json/\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Command line interface tool to convert XLS file to JSON.  
	\item Made for a one-off task during internship. Isn't properly tested.
\end{itemize}
\vspace*{2mm}
{\textbf{Currently working on: rlox}} \hfill {\sl rust}\\link/to/repository\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Following along Crafting Interpreters book. Practically translating Java code to Rust.
\end{itemize}

%==== Education ====%
\header{Education}
\textbf{Telkom University, Sarjana Teknik Telekomunikasi}\hfill Aug 2015 | Apr 2019\\


\begin{tabular}{ l l }
  thesis:       & \textit{Design of WDM VLC in FTTH Network}\\
  publication:  & ejournal.itn.ac.id/index.php/seniati/issue/view/96\\
  GPA:          & 3.65/4.00\\ 
  honor:        & Cum Laude\\
\end{tabular}
\vspace{2mm}

%==== Skills ====%
\header{Familiar}
\begin{tabular}{ l l }
  languages: & python, javascript, rust\\
  tools: & ubuntu, git, npm\\        
  general: & Optical Communication System, Computer Vision, Web Development, Software Testing, \\
  & Agile Methodologies\\                   
\end{tabular}
\vspace{2mm}

\ 
\end{document}
