% LaTeX boilerplates from [resumake.io](https://resumake.io)

\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[margin=1in]{geometry}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Large \scshape {Tubagus Muhammad Reza Handzalah}}\\
	rezahandzalah@gmail.com $\cdot$ +6281312646370 $\cdot$ linkedin.com/in/reza-handzalah\\
\end{center}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{IDEMIA}\hfill Aug 2019 | present\\
\textit{as Software Engineer @ Card Personalization System (CPS), Jakarta Office}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Develops and tests CPS Mobile Card Configurator graphical user interface application.
\end{itemize}
\vspace{1mm}

\textbf{PT Telekomunikasi Indonesia}\hfill Jan 2019 | Jun 2019\\
\textit{as Data Scientist Intern @ Divisi Digital Service}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Contributed to computer vision projects such as Document Recognition with OCR.
	\item The project does the OCR computation in Google Cloud Platform. My contribution was developing the system's command line interface application.
\end{itemize}
\vspace{1mm}



\textbf{PT Radar Telekomunikasi Indonesia} \hfill Apr 2018 | Jun 2018\\
\textit{as Intern}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item GUI project (Microsoft Visual Studio C\#) for radar antenna motor.
  
\end{itemize}

\textbf{Optical Communication System Lab}\hfill Aug 2017 | Aug 2018\\
\textit{as Research Assistant Coordinator} \\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
  \item Organized FTTH Drafter Training, paid optical communication system training event with 30 participants (mostly final-year undergraduate students).
  \item Competed in Ristekdikti PKM. My team managed to get 2 proposals accepted.
  
\end{itemize}


%==== Projects ====%
\header{Projects}
{\textbf{xls2json}} \hfill {\sl Python}\\pypi.org/project/xls2json/\\

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Command line interface tool to convert XLS file to JSON.  
\end{itemize}

\vspace*{2mm}

{\textbf{PixelAdder: Image Restoration based on
}} \hfill {\sl Python, Matlab}\\
{\textbf{Convolutional Neural Network for Intelligent Surveillance Camera}}


\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Gemastik 2018 participant team member.
  \item Built a CNN that maps less recognizable 8x8 pixels face image to 32x32.
  
  
\end{itemize}


\vspace*{2mm}

{\textbf{Computer Vision Course Final Project}} \hfill {\sl Matlab}\\

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Matlab GUI development to demonstrate a given paper.
    \item Paper title: \textit{Single-Image Super-Resolution Based on Rational Fractal Interpolation}
  
\end{itemize}



\vspace*{2mm}

%==== Education ====%
\header{Education}
\textbf{Telkom University}\hfill Aug 2015 | Apr 2019\\
Sarjana Teknik Telekomunikasi\\


\begin{tabular}{ l l }
	thesis:       & \textit{Design of WDM VLC in FTTH Network}\\
	publication:  & ejournal.itn.ac.id/index.php/seniati/article/view/2309\\
  GPA:          & 3.65/4.00\\ 
  honor:        & Cum Laude\\
\end{tabular}
\vspace{2mm}

%==== Skills ====%
\header{Familiar}
\begin{tabular}{ l l }
	languages: & Python, JavaScript, Matlab, Java\\
  tools: & Ubuntu, Git, npm\\        
  general: & Optical Communication System, Computer Vision, Web Development, Software Testing, \\
  & Agile Methodologies\\                   
\end{tabular}
\vspace{2mm}

\header{Online Certifications}
\textbf{ISTQB Foundation Level Certification 2018 (Certified Tester Foundation Level)} \hfill Udemy\\
udemy-certificate.s3.amazonaws.com/pdf/UC-9JD17GC5.pdf\\
\vspace*{2mm}
\textbf{JavaScript Algorithms and Data Structures} \hfill freeCodeCamp\\
freecodecamp.org/certification/tbmreza/javascript-algorithms-and-data-structures\\
\vspace*{2mm}
\textbf{Data Science on the Google Cloud
Platform} \hfill Qwiklabs\\
qwiklabs.com/public\_profiles/a52e3f27-2aaa-405a-bdd4-8bd2c6c2a89b\\


\ 
\end{document}
